Evaluation of +S2 sea ice forecast and some other better title

### 2025-10-06 analysis/paper/access-ice.qmd
Forces sentence wrap

---
title: Evaluation of +S2 sea ice forecast and some other better title
pdf-engine: pdflatex
journal:
  name: tc
author:
  - given_name: Elio 
    surname: Campitelli
    affiliation: "1,2"
    email: elio.campitelli@monash.edu
    corresponding: true
  - given_name: Ariaan 
    surname: Purich
    affiliation: "1,2"
  - given_name: Julie
    surname: Arblaster
    affiliation: "1,2"
  - given_name: Eun-Pa
    surname: Lim
    affiliation: "3"
  - given_name: Matthew
    surname: Wheeler
    affiliation: "3"
  - given_name: Phillip
    surname: Reid
    affiliation: "3"

>>>>

---
editor:
  markdown:
    wrap: sentence
title: Evaluation of +S2 sea ice forecast and some other better title
pdf-engine: pdflatex
journal:
  name: tc
author:
  - given_name: Elio 
    surname: Campitelli
    affiliation: "1,2"
    email: elio.campitelli@monash.edu
    corresponding: true
  - given_name: Ariaan 
    surname: Purich
    affiliation: "1,2"
  - given_name: Julie
    surname: Arblaster
    affiliation: "1,2"
  - given_name: Eun-Pa
    surname: Lim
    affiliation: "3"
  - given_name: Matthew
    surname: Wheeler
    affiliation: "3"
  - given_name: Phillip
    surname: Reid
    affiliation: "3"
